Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging

### 2018-12-31 ms5n17-tlp-mn-180216-001.tex
wording changes
Almost finished...

\documentclass[preprint,12pt]{article}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,authblk,lineno}
%\linenumbers
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}

@@

NMR spectroscopy can provide a useful complementary readout capability 
for microfluidic devices. For example, the metabolic activity of cell cultures 
can be followed non-invasively by NMR throughout the course of the experiment, 
while effects on cell differentiation can still be analysed by a (destructive) 
transcriptomic analysis at the end. Unfortunately, the sensitivity 
of NMR is much lower than that of optical techniques. 
The small volumes involved in microfluidic systems
 (typically in the range of 1~$\mu$l) 
compound this problem. As is well known, the mass limit of detection of 
inductive NMR detectors improves as they are scaled down~\cite{Olson1995}. 
On this basis, a number of different micro-NMR detector designs have been 
proposed and characterised in the literature~\cite{utz2012review,micronmr2014review}. 
In most cases, these are based on micro-solenoid~\cite{SUBRAMANIAN1998,Pines2007}, 
planar~\cite{Maguire2007,dieter2008,EHRMANN200}, or stripline 
detectors~\cite{stripline_jan}. 
Significant research has gone into developing micro-NMR detectors for flow probes, 
where the sample container takes the form of a fixed capillary into which the sample
must be injected. Only a few designs that allow insertion of a removable microfluidic 
device into the detector have been described [REF Graeme, Spengler, Korvink et al].

@@

In the remainder of this paper, we discuss the probe design in more detail, 
and characterise its performance in terms of sensitivity and resolution. 
We also demonstrate its application in microfluidic cell culture, 
protein NMR spectroscopy, and micro-imaging. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Probe Design}
\label{sec:probe-design}
%Figure showing modular probe concept; example of probe base with several inserts\newline
%\begin{itemize}
%	\item Philosophy: use cheap materials and prefab Al profiles wherever possible
%	\item Hold it together with a small number of precision-machined parts
%	\item Generic probe base design that can accommodate a variety of inserts
%	\item Insert: PCB that accommodates both tuning/matching circuitry for up to two channels and the transmission line probe itself
%	\item Tuning and matching capacitors for each channel are part of the probe base
%	\item Connection using standard coaxial RF connectors (SMP)
%	\item Microfluidic chip design; outline
%	\item Design/explosion drawings
%	\item Circuit design for double resonance
%	\item Transmission line connection between tuning/matching of 1H channel and resonator (Smith chart argument)
%	\item 38 mm bore (Bruker NB) and 45 mm bore (Varian/Agilent NB)
%\end{itemize}
\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png} 
\caption{Micrograph of the probe with and without the sleeve.}
\label{fig:probe} 
\end{figure}
The probe assembly design is based on readily and easily available materials and parts 
with minimal need for fabrication of customised parts to avoid any bottlenecks in the 
building process. The probe can be built from scratch with no requirement of any part 
or electronics from commercial NMR probes. 
All parts and electronic components are readily available from commercial sources, 
with the exception of a small number of precision-machined parts which are used 
to hold the assembly together. These can be ordered from commercial prototyping 
manufacturers or machined in-house if mechanical workshop facilities are available.

@@

The base, the scaffold assembly and the tuning and matching PCB all have a free circular 
axial bore providing access from the bottom of the probe, which can be used for 
temperature and environmental control and/or fluidic connections to the sample as
needed.
The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4) and an 
RF-insert (6). The detector used here is based on a planar transmission line geometry 
as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper 
planes each with a constriction at the centre.  This geometry gives rise to an 
electromagnetic eigenmode with a strong anti-node of the magetic field between
the two planes at the site of the constriction. This concentrates the rf field 
and the detection snsitivity
onto the sample area. 
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for the channel separation and primary 
tuning and matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs 
together. 
The probe sheath (not shown here) is connected to the auxiliary disk (2) 
and the scaffold assembly through screws. 
An exchangeable microfluidic device (1) can be inserted from the top of the detector. 
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ, with fluidic connections 
attached inside the magnet. The microfluidic device is held in place by the spacer 
between the two PCB planes coinciding the sample chamber with the constriction on the 
detector.  The 45-degree edges of the device outline help with precise and reliable
alignment.

The RF-insert (6) can be exchanged to tune and match the probe to different frequencies 
at the X channel. As the detector is connected to the probe base through detachable 
connectors, various detectors can be used on the same probe skeleton. 
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.
\par
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
\caption{Dual channel probes with (A) and without (B) modular RF insert (6) for X channel. A has an O.D. of 44.45 mm, in B, circuit elements of X channel are integrated on the PCB itself making it compact (38 mm O.D.). Detachable SMP connectors (14) are used to connect the RF insert (6) and also the assembled NMR detector. The cost and effort to make a new detector are minimal so, various detectors could be made for various X channel frequencies.}
\label{fig:ProbePhoto}
Figure~\ref{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 6. However, in (B) the circuitry of the RF insert (6) is manufactured on the PCB plane (5). Inclusion of the circuitry of 6 on 5 makes the design more compact. Probe (A) is compatible with Varian 600 ultra shield 14.1 T magnet having an outer diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an outer diameter (O.D.) of 38 mm including the sheath, is designed to fit inside a Bruker narrow bore shim stack. Probe (B) also fits inside a Bruker micro-imaging gradient unit. Naturally, B can also be used with wide bore magnets with spacers or gradient stack to keep the probe centred .\par
The microfluidic devices are made from thermally bonded PMMA sheets. The sample chamber and fluidic network are made in the middle layer. The middle layer is sealed in between the bottom and the top layers with inlet and outlet in the top layer. A flow can be introduced from the inlet and outlet of the device for flow studies or sample exchange. The fluidic network on the device can be made freely with the only constrained on the overall size of the device. Other layers can be employed to allow parallel flow as long as the total thickness remains below 1mm.\par
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png} 
\caption{Microfluidic devices for different applications compatible with the current setup. From left: Devices for perfusion of tissue slice on a chip, peristaltic pumping to induce flow, hydrogenation on a chip, droplet generator, simple design to fill the sample chamber and, to grow cells on the device.}
\label{fig:device} 
The circuit for a double resonance probe is based on design shown in figure~\ref{fig:circuit}. The size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger sample volumes for some cases. Primary tuning of the detector is performed through the circuit elements (mainly C$_6$). The detector is connected to the secondary tuning and matching capacitors with the transmission lines on the PCB planes. As all the circuit elements are assembled on the PCB planes, the transmission lines on the PCB have lengths similar to the detector. Hence transmission lines may become a part of the resonance circuit and can severely affect the probe performance. To avoid this problem a series capacitor (C$_5$) was included with the transmission line just before the detector to adjust the impedance of transmission line to 50~$\Omega$. In this situation the detector is matched by the transmission line and secondary tuning and matching capacitors can be used for fine tuning and matching.\par
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
\caption{Circuit diagram of the double resonance probe. Proton frequency is feed in from the left (port 2) and X frequency is feed in from right (port 7).}
\label{fig:circuit}
\section{Materials and Methods}
%	\item Design process (SolidWorks, etc)
%	\item Manufacture of parts (ProtoLabs, some in-house machining)
%	\item Optimisation of resonator geometry (ref Graeme's paper)
%	\item Design and optimisation of tuning/matching circuitry (Mathematica routines)
%	\item Design of PCB using KiCAD
%	\item PCB material and manufacture
%	\item Assembly, soldering
%	\item NMR spectrometers and parameters
%	\item samples
%The probe base platform is made up of 6 mm thick aluminium sheet [$l\times w \times h = 150 mm\times 150mm\times 75mm$]. Probe sleeve has diameter of 38 mm compatible with Bruker 500 MHz. The probe was used with a spacer on varian 600 MHz.
All the parts and the probe assembly were designed and simulated on Solidworks (Solidworks, Dassault Syst\`{e}mes). The prefabricated aluminium profiles (base platform, scaffold aluminium tubes, probe sleeve) were made from 6061-T3 alloy and were obtained from Aluminum Warehouse, UK to build the probe skeleton. A few customised precision-machined parts (scaffold support disks, top disk) were obtained from ProtoLabs (Telford, UK) after providing CAD files. A small number parts were machined in-house (detector support rods, auxiliary support disks). All the electronic components and the semi rigid transmission lines were purchased from Digikey. Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment (Wendover, UK). Microfluidic devices were designed on AutoCAD. PMMA sheets were cut to desired size and functionality (holes or channels) through a laser cutter (HPC Laser L3040). The fluidic channels were cut or scored in a 0.5 mm thickness PMMA sheet. The device is made by thermally bonding PMMA sheets using the protocol described in~\cite{yilmaz_bonding}.\par
Dimensions of the detector were calculated from the simulation described in~\cite{gream_2016}. The probe circuit for the double resonance probe was simulated on Mathematica using a symbolic analysis network code to asses the performance of both the channels~\cite{gream-thesis}.\par
The probe circuit was compiled in KiCAD to design the PCB layout. The PCB layout was provided to beta-layout (Aarbergen Germany) and P.W. Circuits LTD (Wigston , UK) to manufacture the PCBs. Easily and inexpensively available FR4 was used for PCB manufacturing for (figure~\ref{fig:ProbePhoto} A). RO3035 from Rogers corporation was used for PCBs used in (figure~\ref{fig:ProbePhoto} B).\par
The probe skeleton was assembled by holding the prefabricated aluminium profiles with precision-machined parts and screws. Semi-rigid transmission lines were then threaded through the skeleton. The base PCB plate was soldered on top of the semi-rigid transmission lines. The detector planes (3 and 5) were soldered together separately with the required electronic components characterise by network analysis. Minor changes were made to the values of the probe electronic components to optimise the probe performance in practise.\par
NMR experiments were performed on Varian VNMRS console on a Varian 600 ultra shield 14.1 T magnet. Spectra in figure~\ref{fig:lineshape} and \ref{fig:media-spec} were obtained with water presaturation followed by a 90$^{\circ}$ pulse. Spectrum in figure~\ref{fig:1H-nutation} was acquired with increasing the pulse length. Spectrum in figure~\ref{fig:15N-nutation} was acquired using pulse sequence described in~\cite{bax_indirect}. Sodium acetate and $^{15}$N labeled urea were purchased from Merek and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par
Imaging experiments were performed on Bruker AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet. To obtain the tissue slices first a core of 8 mm diameter was extracted using a biopsy punch from the liver. PCLS of thickness 250-300 $\mu$m were prepared using a Krumdieck Tissue slicer. Circular slices of 3 mm diameter were then cut from this slice using a smaller punch.The slices were put in the incubator for 2 hours before imaging to allow equilibrium.
\section{Results and Discussion}
%	\item Tuning/matching/channel separation
%	\item tuning range (different field strengths)
%	\item Sensitivity calibration
%	\item Resolution
%	\item RF efficiency, B1 homogeneity
%	\item Example spectra to illustrate versatility:
%		\begin{itemize}
%		\item Growth media (1H), cell culture
%		\item Comparison of spectra obtained at 300, 500, 600 MHz
%		\item HSQC (13C, 15N)
%		\item Liver slice image
%		\end{itemize}
A double channel probe allows heteronuclear NMR experiments which are essential for many applications like protein structure determination. The current probe can be simultaneously operated at 2 frequencies. The probe can be tuned to protons and one X channel ($^{13}$C or $^{15}$N) frequencies at a time. As already explained, the X channel tuning frequency can be changed by simply exchanging an rf-insert or the complete detector. Figure~\ref{fig:tandm} shows the measured tuning and matching curves at different proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz) corresponding to the larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14 T and 11.7 T respectively. The measurements were performed in the pairs of 600 MHz and 60 MHz and, 500 MHz and 125 MHz. The loaded Q factors are 42, 49, 32, 36 at 600 MHz, 500 MHz, 125 MHz and, 60 MHz respectively. Channel separation is better than 15 decibels at all operating frequencies and thus sufficient to perform decoupling during experiments.\par
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png} 
\caption{Experimental tuning and matching curves measured at 600 MHz, 500 MHz, 60 MHz ($^{15}$N frequency at 14 T) and, 125 MHz ($^{13}$C frequency at  and 11.7 T). Probe can be tuned to 2 frequencies at a time, above results were measured in pairs of 600 MHz with 60 MHz and 500 MHz with125 MHz. Decoupling can be performed at all the frequencies as the channel separation is better than 15 decibels at all frequencies.}
\label{fig:tandm} 
Initially FR4 PCB material was used to make detector assembly because of its low cost and easy availability. B$_0$ field maps of the sample chamber generated from gradient echo images using these detectors showed inhomogeneities in the B$_0$ field. To avoid inhomogeneities and therefore to achieve better resolution, detectors were made from RO3035 material from Rogers corporation. Though RO3035 provides better resolution it is more expensive and takes longer to obtain compared to FR4. A new detector design can first be tested using FR4 material and the optimised design can be made from RO3035.\par
$^1$H nutation diagram of water peak for a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz is shown figure~\ref{fig:1H-nutation}. RF field is highly homogeneous with 810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% at 600~MHz. The probe can generate 100 kHz RF-field for an input power of 100 W both at 600 MHz and 500 MHz corresponding to RF field efficiency (B$_{1}/\sqrt{power}$) of 10 kHz/$\sqrt{W}$ . $^{15}$N nutation detected on protons for the same sample is shown in figure~\ref{fig:15N-nutation}. An RF field of 6 kHz at 60 MHz can be generated at 14 T for $^{15}$N and an RF field of 14 kHz at 125 MHz can be generated at 11.7 T for $^{13}$C with measurements. The power used at the X channel was more than 100 W still no signs of arcing were observed in the NMR spectrum.\par
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png} 
\caption{$^1$H nutation acquired for water peak from a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz. The 810$^{\circ}$/90$^{\circ}$ ratio is more than 90\% at 600~MHz. The 90$^{\circ}$ pulse length is below 2.5 $\mu$ sec corresponding to 100 kHz radio-frequency field for an input power of 100 W. Similar B$_{1}$ efficiency and homogeneity was observed at 500 MHz}
\label{fig:1H-nutation} 
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-15-Nnutation-171215-003.png} 
\caption{$^{15}$N nutation detected on proton of $^{15}$N-urea dissolved in water acquired at 14 T corresponding to 60 MHz frequency. A radio-frequency field of 6~kHz can be generated at 60~MHz.}
\label{fig:15N-nutation} 
Figure~\ref{fig:lineshape} shows a spectrum of 130 mM Na-acetate peak dissolved in H$_2$O acquired after water presaturation at 600 MHz with 32 averages. The figure in the inset shows expanded view of the base of the acetate peak. Carbon satellites can be seen well above noise level. The orange curve corresponds to a Lorentzian lineshape with full width at half maximum of 3.35 Hz. Limit of detection $nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ is  1.18 nmol s$^{1/2}$ at 600 MHz for the acetate sample. The measured LOD is found to be better than the calculated LOD in~\cite{gream_2016} for 600 MHz.\par

>>>>

\documentclass[preprint,12pt]{article}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,authblk,lineno}
%\linenumbers
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\todo}[1]{{\color{red}\textbf{#1}}}
\newcommand{\fig}[1]{Fig.~\ref{#1}}

@@

NMR spectroscopy can provide a useful complementary readout capability 
for microfluidic devices. For example, the metabolic activity of cell cultures 
can be followed non-invasively by NMR throughout the course of the experiment, 
while effects on cell differentiation can still be analysed by a (destructive) 
transcriptomic analysis at the end. Unfortunately, the sensitivity 
of NMR is much lower than that of optical techniques. 
The small volumes involved in microfluidic systems
 (typically in the range of 1~$\mu$l) 
compound this problem. As is well known, the mass limit of detection of 
inductive NMR detectors improves as they are scaled down~\cite{Olson1995}. 
On this basis, a number of different micro-NMR detector designs have been 
proposed and characterised in the literature~\cite{utz2012review,micronmr2014review}. 
In most cases, these are based on micro-solenoid~\cite{SUBRAMANIAN1998,Pines2007}, 
planar~\cite{Maguire2007,dieter2008,EHRMANN200}, or stripline 
detectors~\cite{stripline_jan}. 
Significant research has gone into developing micro-NMR detectors for flow probes, 
where the sample container takes the form of a fixed capillary into which the sample
must be injected. Only a few designs that allow insertion of a removable microfluidic 
device into the detector have been described \todo{REF Graeme, Spengler, Korvink et al}.

@@

In the remainder of this paper, we discuss the probe design in more detail, 
and characterise its performance in terms of sensitivity and resolution. 
We also demonstrate its application in microfluidic cell culture, 
protein NMR spectroscopy, and micro-imaging. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Probe Design}
\label{sec:probe-design}
%Figure showing modular probe concept; example of probe base with several inserts\newline
%\begin{itemize}
%	\item Philosophy: use cheap materials and prefab Al profiles wherever possible
%	\item Hold it together with a small number of precision-machined parts
%	\item Generic probe base design that can accommodate a variety of inserts
%	\item Insert: PCB that accommodates both tuning/matching circuitry for up to two channels and the transmission line probe itself
%	\item Tuning and matching capacitors for each channel are part of the probe base
%	\item Connection using standard coaxial RF connectors (SMP)
%	\item Microfluidic chip design; outline
%	\item Design/explosion drawings
%	\item Circuit design for double resonance
%	\item Transmission line connection between tuning/matching of 1H channel and resonator (Smith chart argument)
%	\item 38 mm bore (Bruker NB) and 45 mm bore (Varian/Agilent NB)
%\end{itemize}
\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png} 
\caption{Micrograph of the probe with and without the sleeve.}
\label{fig:probe} 
\end{figure}
The probe assembly design is based on readily and easily available materials and parts 
with minimal need for customised fabrication.
All mechanical and electronic components are readily available from commercial sources, 
with the exception of a small number of precision-machined parts which are used 
to hold the assembly together. These can be ordered from commercial prototvaiyping 
manufacturers or machined in-house if mechanical workshop facilities are available.

@@

The base, the scaffold assembly and the tuning and matching PCB all have a free circular 
axial bore providing access from the bottom of the probe, which can be used for 
temperature and environmental control and/or fluidic connections to the sample as
needed.
The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4) and an 
RF-insert (6). The detector used here is based on a planar transmission line geometry 
as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper 
planes, each with a constriction at the centre.  This geometry gives rise to an 
electromagnetic eigenmode with a strong anti-node of the magnetic field between
the two planes at the site of the constriction. This concentrates the rf field 
and the detection sensitivity
onto the sample area. 
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for channel separation and primary 
matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs 
together at the top, and forms the top end of the probe assembly.
The probe sheath (not shown here) is fixed to the auxiliary disk (2) 
and the scaffold assembly with screws. 
An exchangeable microfluidic device (1) can be inserted from the top of the detector. 
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ. 
The microfluidic device is held in place by the spacer 
between the two PCB planes coinciding the sample chamber with the constriction on the 
detector.  The 45-degree edges of the device outline help with precise and reliable
alignment. 
Since the detector assembly is attached to the probe base through SMP 
connectors, it can easily be exchanged. 
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.
\par
\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
\caption{Dual channel probes with (A) and without (B) modular RF insert (6) for X channel. 
A has an O.D. of 44.45 mm, in B, circuit elements of X channel are integrated on the 
PCB itself making it compact (38 mm O.D.). Detachable SMP connectors (14) are used to 
connect the RF insert (6) and the detector assembly. }
\label{fig:ProbePhoto}
\end{figure}
Figure~\ref{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) 
for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 6. 
However, in (B) the circuitry of the RF insert (6) is integrated on the PCB plane (5), 
making the design more compact.
 Probe (A) is compatible with a Varian 600 ultra ) of
shield 14.1 T magnet, with anouter diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an 
outer diameter (O.D.) of 38 mm including the sheath, is designed to fit inside a 
Bruker narrow bore shim stack. 
Probe (B) also fits inside a Bruker micro-imaging gradient unit. Naturally, B can also be used with 
wide bore magnets with spacers or gradient stack to keep the probe centred.

Microfluidic devices are made from thermally bonded PMMA sheets as described in detail elsewhere. [REF]
Briefly, the devices consist of a 0.5~mm thick middle layer between a top- and bottom layer of 
0.2~mm thickness each. The sample chamber and fluidic network are cut into the middle layer.
The fluidic network on the device can be designed freely as long as the overall shape of the
device is preserved, and the location of the sample chamber is maintained.

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png} 
\caption{Microfluidic devices for different applications compatible with the current setup. 
From left: Devices for perfusion of tissue slice on a chip, peristaltic pumping to induce flow, 
hydrogenation on a chip, droplet generator, simple design to fill the sample chamber and, 
to grow cells on the device.}
\label{fig:device} 
\end{figure}

The double resnance circuit is based on the design shown in figure~\ref{fig:circuit}. 
%The size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger 
%sample volumes for some cases. 
The transmission line detector is tuned to the desired proton 
Larmor frequency by chip capacitors located at its four corners, 
as well as a non-magnetic trimmer capacitor ($C_6$). Two primary 
matching capacitors ($C_5$ and $C_5'$) bring the impedance into the 
vicinity of 50$\Omega$. A short microstrip 
with a specific impedance of 50$\Omega$ 
on the PCB then provides a connection to the secondary tuning and matching elements on the TMPCB ($C_1$ and $C_2$).
The lower frequency channel is connected to the detector through a high-frequency band reject ($C_7$, $L_7$).
Tuning is achieved by $L_1$ and $C_4$, which are both located on the exchangeable insert, in combination with
the complex admittance of the detector at the X channel frequency.
To maximise efficiency, $L_1$ should have as high a $Q$-factor as possible. We have
used commercially available flat copper coils of 8 mm diameter and 3.5 turns \todo{check values} in the case of 
\textsuperscript{15}N at 60 MHz. Tuning to \textsuperscript{13}C, either at 125 or at 150 MHz 
could be achieved without $L_1$.

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
\caption{Circuit diagram of the double resonance probe. 
Proton frequency is fed in from the left (port 2) and X frequency is fed in from right (port 7).}
\label{fig:circuit}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
%\begin{itemize}
%	\item Design process (SolidWorks, etc)
%	\item Manufacture of parts (ProtoLabs, some in-house machining)
%	\item Optimisation of resonator geometry (ref Graeme's paper)
%	\item Design and optimisation of tuning/matching circuitry (Mathematica routines)
%	\item Design of PCB using KiCAD
%	\item PCB material and manufacture
%	\item Assembly, soldering
%	\item NMR spectrometers and parameters
%	\item samples
%\end{itemize}
%The probe base platform is made up of 6 mm thick aluminium sheet [$l\times w \times h = 150 mm\times 150mm\times 75mm$]. Probe sleeve has diameter of 38 mm compatible with Bruker 500 MHz. The probe was used with a spacer on varian 600 MHz.
All the parts and the probe assembly were designed in Solidworks (Solidworks, Dassault Syst\`{e}mes). 
Prefabricated profiles made from 6061-T3 aluminium (Aluminum Warehouse, UK) were used for the
 mechanical structure of the probe
(base platform, scaffold tubes, sleeve). 
A few customised precision-machined parts (scaffold support disks, top disk) were obtained from 
ProtoLabs (Telford, UK) after providing CAD files. A small number parts were machined in-house
 (detector support rods, auxiliary support disks). 
 All  electronic components including semi-rigid transmission lines were purchased from DigiKey Ltd. 
 Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment (Wendover, UK). Microfluidic 
devices were designed on AutoCAD. PMMA sheets were cut to desired size and functionality (holes or channels) using a 
laser engraving system  (HPC Laser L3040), 
and then bonded using the protocol described in~\cite{yilmaz_bonding}.

The precise dimensions of the detector were optimised for a given sample volume using 
finite element calculations in COMSOL, as described in \cite{gream_2016}. 
The RF response of the probe circuit was simulated using a symbolic  
network analysis code~\cite{gream-thesis} in order to estimate appropriate component values. Final tuning
was done by trial and error using an Agilent FieldFox 4 GHz network analyser. 
PCB layouts were designed using KiCAD, and then sent to
beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) 
for manufacturing. Easily and inexpensively available FR4 PCB material
(\fig{fig:ProbePhoto} A) proved adequate for some purposes, but limited resolution to about 10 Hz.
A high-quality Teflon-based RF PCB material (RO3035, Rogers Corp., USA) was therefore used for optimal 
performance in both sensitivity and resolution (\fig{fig:ProbePhoto} B).
The probe skeleton was assembled from prefabricated aluminium tubes with the  precision-machined scaffold
disks using brass screws. Semi-rigid transmission lines were then threaded through the tubes, and the TMPCB plate was 
soldered on top. The detector planes (3 and 5) and the PMMA spacer between them were assembled using short bits
of 0.5~mm magnet wire, which were soldered to the appropriate pads in the four corners of the detector structure.

NMR experiments were performed on a Varian VNMRS console attached to a Varian 600 ultra shield 14.1 T magnet.  
Imaging experiments were performed on Bruker AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T 
magnet. 
Sodium acetate and $^{15}$N labeled urea were purchased from Merek \todo{Address?} and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par

Precision-cut murine liver slices (PCLS) were obtained by first extracting a tissue core of 8 mm diameter 
using a biopsy punch. PCLS of 250-300 $\mu$m thickness were cut from the core using a Krumdieck Tissue slicer, 
and then reduced to 3~mm diameter using a smaller punch.The slices were incubated in well-plates at 37$^\circ$C and 80\%
O\textsubscript{2}, 4\% CO\textsubscript{2}
for 2 hours before imaging.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion}
The spectra in \fig{fig:lineshape} and \fig{fig:media-spec} were obtained with water presaturation followed by a 90$^{\circ}$ pulse. Spectrum in figure~\ref{fig:15N-nutation} was acquired using pulse sequence described in~\cite{bax_indirect}.

%\begin{itemize}
%	\item Tuning/matching/channel separation
%	\item tuning range (different field strengths)
%	\item Sensitivity calibration
%	\item Resolution
%	\item RF efficiency, B1 homogeneity
%	\item Example spectra to illustrate versatility:
%		\begin{itemize}
%		\item Growth media (1H), cell culture
%		\item Comparison of spectra obtained at 300, 500, 600 MHz
%		\item HSQC (13C, 15N)
%		\item Liver slice image
%		\end{itemize}
%\end{itemize}
The probe is designed for double resonance, with proton-detected experiments in mind. The circuit is optimised
for efficiency and sensitivity at the high-frequency channel, while allowing RF pulses to be applied
at the X frequency as well. As already explained, the X channel tuning frequency can be changed by simply
 exchanging either only a small RF-insert or the complete detector assembly. 
 \fig{fig:tandm} shows the measured reflection and transmission scattering coefficients ($S$-parameters) as a 
 function of frequency for two combinations of 
 proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz), 
 corresponding to the Larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14 T and 11.7 T respectively. 
 The measurements were performed in the pairs of 600 MHz and 60 MHz and 500 MHz and 125 MHz. The loaded $Q$ factors,
 determined from the -3dB points of the reflection curves, are 42, 49, 32, 36 at 600 MHz, 500 MHz, 
 125 MHz and, 60 MHz respectively. The channel separation is better than -15dB at all operating frequencies.

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png} 
\caption{
Experimental tuning and matching curves measured at 600 MHz, 500 MHz, 
60 MHz (\textsuperscript{15}N frequency at 14 T) and 125 MHz (\textsuperscript{13}C frequency at  and 11.7 T). 
Probe can be tuned to 2 frequencies at a time, above results were measured in 
pairs of 600 MHz with 60 MHz and 500 MHz with125 MHz. Decoupling can be performed at all the 
frequencies as the channel separation is better than 15 decibels at all frequencies.}
\label{fig:tandm} 
\end{figure}

Initially FR4 PCB material was used for the detector assembly because of its low cost and easy availability. 
B$_0$ field maps of the sample chamber obtained from gradient echo images using these detectors 
showed inhomogeneities in the B$_0$ field due to the glass fibre rovings in FR4's composite backing (not shown).
To avoid these inhomogeneities and therefore to achieve better resolution, 
detectors were made from RO3035 material. While RO3035 provides better resolution, it is more expensive 
and takes longer to obtain compared to FR4. 
It therefore makes sense to first prototype new detector designs in FR4, and only use the more expensive RO3035 
once the design has been validated.

\fig{fig:1H-nutation} shows the $^1$H nutation diagram of the water peak in an aqueous solution of 
100~mM $^{15}$N-urea  measured at 600~MHz. The RF field shows good homogeneity, with a 810$^{\circ}$/90$^{\circ}$ 
ratio of more than 90\%. The probe generates 100~kHz nutation frequency from 100~W input power both at 
600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$) of 10 kHz/$\sqrt{W}$. 
The detector geometry has been optimised for a sample volume of 5~$\mu$l. It compares reasonably well to
the value of 22 kHz/$\sqrt{W}$ that has been reported by Finch et al.\todo{REF} for single-frequency detector 
of half this size at a Larmor frequency of 300~MHz.

The probe is not sensitive enough to make direct detection of $^{15}$N signals practical. Nutation at the
$^{15}$N frequency was therefore detected indirectly using coherence transfer to protons. 
\fig{fig:15N-nutation} shows the results. Using 100~W of input power \todo{verify power setting} 
produces nutation frequencies of 6 kHz for $^{15}$N and 14 kHz for $^{13}$C. 
No signs of arcing were obseved at this power level for pulses up to 1~ms duration.
